% CS 289A Final Report — Lesion-Focused Classification for Skin Cancer Detection
%
% Drafting notes:
%   - Single-column article, ~6-10 pages (instructions/sp26-grad-project.pdf).
%   - Plan: swap in icml2024.sty (or similar) before submission. Vanilla article keeps
%     this compilable in any TeX setup while drafting.
%   - \todo{...} markers flag sections that still need experiments, figures, or numbers.
%     Real numbers below come from metrics/classification_bootstrap_metrics.csv (HEAD).

\documentclass[10pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}
\usepackage{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{cleveref}
\usepackage{caption}

% Lightweight TODO marker (no todonotes dependency).
\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO:} #1\textbf{]}}}

\title{Lesion-Focused Classification for Skin Cancer Detection:\\
Does Background Suppression Help Generalization?}
\author{Tobias Roemer \and Thomas Lee \and Leo Li\\
CS 289A, Spring 2026}
\date{May 15, 2026}

\begin{document}
\maketitle

\begin{abstract}
Skin lesion classifiers trained end-to-end on dermoscopic images may rely on
non-lesion context --- skin texture, hair, lighting, imaging artifacts --- rather
than on the lesion itself. We test whether \emph{explicitly localizing the lesion
before classification} improves performance and out-of-distribution
generalization. We train a DeepLabV3-ResNet50 segmenter on ISIC 2018 lesion
masks, use it to produce lesion-on-white versions of every HAM10000 image, and
fine-tune four classifiers (a basic CNN, a small ViT, a from-scratch ResNet, and
an ImageNet-pretrained ResNet-50) on the full-image and lesion-white inputs
under matched training conditions. We evaluate on a held-out HAM10000 test set
and on PAD-UFES-20, a clinical-photograph dataset with substantially different
imaging characteristics, with sensitivity and specificity reported using
non-parametric bootstrap confidence intervals at a target sensitivity of
$0.90$. \todo{One-sentence punchline once we settle on the headline number ---
likely: lesion-white inputs preserve in-domain performance and improve specificity
on PAD-UFES-20 for non-pretrained models, but the ImageNet-pretrained ResNet-50
narrows the gap.}
\end{abstract}

% ============================================================================
\section{Problem Definition}
\label{sec:problem}

Skin lesion classification from dermoscopic images is an established benchmark
problem in medical computer vision and a practical target for early skin cancer
screening~\citep{esteva2017dermatologist, tschandl2018ham10000}. The standard
pipeline fine-tunes a convolutional network on the raw lesion image and predicts
the diagnostic label directly. A persistent concern with this pipeline is that
the network does not learn lesion-specific features but instead exploits
correlated context: the dermoscope vignette, the presence of rulers or ink
markings, body-site appearance, the patient's skin tone, or lighting
artifacts~\citep{winkler2019association, bissoto2019skin}. Such shortcuts can
produce high accuracy on the training distribution but fail when the imaging
setup changes, which is precisely what happens when a model trained on
hospital-grade dermoscopy is asked to score a smartphone photograph.

We ask a single experimental question:

\begin{quote}
\emph{Does explicitly localizing the lesion --- so that the classifier only sees
the lesion pixels on a uniform background --- improve binary
benign-vs-malignant classification, both in-distribution (HAM10000) and under
distribution shift to a different imaging modality (PAD-UFES-20)?}
\end{quote}

We isolate the effect of lesion-focusing by holding everything else constant
between the full-image and lesion-focused pipelines: the same backbone
architectures, the same training data, the same augmentation, the same loss,
the same threshold-selection procedure, and the same evaluation splits and
bootstrap protocol. The only thing that changes is whether the input has its
non-lesion background replaced with white before training and inference.

% ============================================================================
\section{Connection to Course Content}
\label{sec:course}

This project draws on several concepts covered in lecture:
\begin{itemize}
  \item \textbf{Convolutional networks and transfer learning.} Our baselines
  are small CNN and ResNet architectures, and our strongest model is an
  ImageNet-pretrained ResNet-50 fine-tuned in a two-phase
  schedule~\citep{he2016deep}.
  \item \textbf{Vision Transformers.} We include a small ViT
  baseline~\citep{dosovitskiy2020vit} trained from scratch under the same
  conditions to test whether the lesion-focusing effect is architecture-specific.
  \item \textbf{Imbalanced classification.} HAM10000 has roughly four times
  more benign than malignant overlap-label cases. We use
  \texttt{BCEWithLogitsLoss} with \verb|pos_weight| equal to the
  negative-to-positive ratio in the training split and select the decision
  threshold on the validation set to hit a target sensitivity.
  \item \textbf{Generalization and distribution shift.} The lesion-focused
  pipeline is, in effect, a hand-coded invariance: we strip background pixels
  so the classifier cannot use them. The OOD evaluation on PAD-UFES-20 is a
  direct test of whether that invariance is useful.
  \item \textbf{Bootstrap uncertainty quantification.} We report 95\%
  bootstrap CIs (5000 resamples) for sensitivity and specificity rather than
  point estimates, so claims about which model is ``better'' can be checked
  against confidence intervals.
\end{itemize}

% ============================================================================
\section{Prior Work}
\label{sec:prior}

\paragraph{End-to-end skin lesion classification.}
\citet{esteva2017dermatologist} showed dermatologist-level skin-cancer
classification with a single InceptionV3 fine-tuned on $\sim$130k dermoscopic
and clinical images. Subsequent work on the ISIC challenge datasets
\citep{codella2019isic, combalia2019bcn20000} extended this to deeper networks,
ensembles, and multi-task training. These models classify directly from the full
image.

\paragraph{Shortcut learning in dermoscopy.}
Several studies have documented that dermoscopic classifiers rely on
non-lesion features. \citet{winkler2019association} showed that surgical ink
markings systematically biased malignancy predictions.
\citet{bissoto2019skin} found that classifiers retained substantial accuracy
when the lesion itself was masked out, indicating heavy use of context cues.
This motivates the question we study: does explicitly removing background
context help generalization?

\paragraph{Lesion segmentation as a preprocessing step.}
The ISIC 2018 Task 1 challenge~\citep{codella2019isic} popularized binary
lesion segmentation, with U-Net and DeepLabV3 variants~\citep{chen2017deeplab}
performing well. Several skin classification pipelines have used segmenters
as an attention or cropping stage~\citep{yu2017automated, gonzalez2018dermaknet},
but typically as part of a multi-task or multi-stream architecture rather than
as a controlled comparison.

\paragraph{Cross-dataset evaluation.}
Generalization across dermoscopy and clinical-photograph datasets has been
studied directly in works such as
\citet{pacheco2020pad, daneshjou2022disparities}, which find non-trivial drops
between in-distribution and OOD test performance. PAD-UFES-20 is a useful test
bed for the present study because its images come from smartphone cameras under
unstandardized conditions, so the non-lesion context is qualitatively different
from HAM10000.

\paragraph{What is missing.} What we did not find is a clean, controlled,
matched-conditions comparison of full-image vs.\ lesion-focused classification
across multiple architectures with the same training pipeline and OOD test set.
That is the gap our contribution fills.

% ============================================================================
\section{Approach}
\label{sec:approach}

\subsection{Datasets}
\label{sec:data}

\textbf{HAM10000}~\citep{tschandl2018ham10000} contains 10{,}015 dermoscopic
images across seven diagnostic categories. We restrict to the five labels
that have a meaningful counterpart in PAD-UFES-20 (\verb|akiec, bcc, bkl, mel,
nv|) and map them to a binary benign/malignant target using the standard
clinical grouping (\verb|bkl, nv| $\to$ benign; the rest $\to$ malignant).
We stratify-split by diagnosis into train/val/test (70/15/15, seed 42),
yielding $|D_{\text{test}}|=1464$ HAM images with 293 malignant and 1171
benign cases.

\textbf{ISIC 2018 Task 1}~\citep{codella2019isic} provides binary lesion masks
for $\sim$2{,}600 dermoscopic images. We use it to train the segmenter that
generates lesion masks for HAM10000.

\textbf{PAD-UFES-20}~\citep{pacheco2020pad} contains 2{,}298 clinical
(smartphone) photographs labeled across six diagnoses. We keep records whose
diagnosis maps onto the same five HAM categories above and apply the same
benign/malignant mapping, yielding 2{,}106 images for cross-domain evaluation
(1{,}627 malignant, 479 benign --- the class balance is essentially flipped
relative to HAM10000).

\subsection{Lesion Segmentation}
\label{sec:seg}

We train a DeepLabV3-ResNet50~\citep{chen2017deeplab} for binary lesion
segmentation on ISIC 2018 Task 1 at $320\times320$, with the classifier and
auxiliary heads reduced to one output channel. Optimization uses AdamW
($\text{lr}=10^{-4}$) with cosine annealing over 40 epochs, batch size 8, the
standard ImageNet normalization, and light geometric and color augmentation
(flips, $k\cdot 90^\circ$ rotations, color jitter). The model selected on
validation IoU reaches \textbf{test Dice $0.909$ and test IoU $0.857$}
(epoch 14; see \verb|metrics/segmentation_deeplabv3_resnet50_metrics.csv|).

To produce lesion-focused inputs, we run the trained segmenter over every
HAM10000 image, threshold the predicted probability map at $0.5$, and use the
mask to composite the original image onto a white background. We do the same
for PAD-UFES-20.

\subsection{Classifiers}
\label{sec:cls}

We train four binary classifiers under identical conditions:
\begin{itemize}
  \item \textbf{BasicCNN.} A 4-block conv stack with batch norm, ReLU, max
  pooling, and dropout, followed by global average pooling and an MLP head.
  \item \textbf{ViT (small).} A from-scratch ViT with patch size 16,
  embedding dimension 192, depth 6, 6 heads, MLP dimension 384, dropout 0.15.
  \item \textbf{SimpleResNet.} A from-scratch ResNet with four stages of
  basic blocks ($32\to64\to128\to256$ channels).
  \item \textbf{Pretrained ResNet-50.} ImageNet-initialized
  ResNet-50~\citep{he2016deep} with a replaced binary head. Training uses a
  two-phase schedule: the head is trained alone for the first 6 epochs while
  the backbone is frozen, then \texttt{layer4} is unfrozen and trained at a
  smaller learning rate ($10^{-5}$) for the remainder. Batch-norm modules are
  kept in eval mode whenever the backbone is frozen.
\end{itemize}

All classifiers take a $224\times224$ RGB image, output a single logit, and are
trained with \verb|BCEWithLogitsLoss| using
\verb|pos_weight = #benign_train / #malignant_train|. Optimization is AdamW
(weight decay $10^{-4}$) with cosine annealing over 60 epochs and early
stopping (patience 20) on the validation specificity at target sensitivity.
The training augmentation pipeline is: resize to $1.15\times$, random
resized crop, horizontal/vertical flips, $\pm 45^\circ$ rotation, small
affine translation/scale/shear, mild perspective, color jitter, occasional
grayscale conversion, and mild Gaussian blur, followed by ImageNet
normalization.

\subsection{Threshold selection and evaluation}
\label{sec:eval}

A binary classifier's operating point matters more than its raw accuracy in a
clinical setting. We fix a \emph{target sensitivity} of $0.90$ and, on the
validation set, sweep all candidate thresholds (the empirical score values plus
$\{0,1\}$) to find the threshold that achieves at least $0.90$ sensitivity with
the highest possible specificity. We save the checkpoint with the best such
validation specificity and re-tune the threshold on validation scores from that
checkpoint before applying it to the test set. The same protocol is applied
identically to every model.

We report sensitivity and specificity at this operating point, together with
95\% bootstrap confidence intervals (5000 resamples, seed 42) constructed by
resampling the test set with replacement.

\subsection{Cross-domain evaluation}
We apply each HAM10000-trained classifier to PAD-UFES-20 \emph{without
retraining}: the model trained on HAM10000 full images is evaluated on
PAD-UFES-20 full images, and the model trained on HAM10000 lesion-white images
is evaluated on PAD-UFES-20 lesion-white images (generated with the same ISIC
segmenter). For reference we also train a separate ResNet directly on a
PAD-UFES-20 train split so we know what an in-domain PAD model looks like.

\subsection{Implementation and infrastructure}
The codebase is Python 3.11 with PyTorch and torchvision. Each $(model_type,
image_source)$ pair is launched by a thin wrapper that calls a shared trainer
(\verb|src/training/ham10000_training.py|) so the four architectures share
exactly the same data, loss, scheduler, threshold-selection, and logging code.
Training runs on a single GPU on PSC Bridges-2 via SLURM
(\verb|submit/submit_full_pipeline.sh| chains the entire pipeline with
\verb|--dependency=afterok|). All experiments are logged to Weights \& Biases.

% ============================================================================
\section{Our Contribution}
\label{sec:contrib}

The contribution of this project is a \emph{controlled, matched-conditions
comparison} of full-image vs.\ lesion-focused classification across four
architectures, evaluated both in-distribution (HAM10000) and under a real
distribution shift (PAD-UFES-20). Concretely:

\begin{enumerate}
  \item We pair each backbone with itself: every architecture is trained twice,
  once on full HAM10000 images and once on lesion-white HAM10000 images, with
  every other knob held fixed. This isolates the effect of the lesion-focusing
  preprocessing.
  \item We use a \emph{single, automatically-derived} lesion mask (from a
  DeepLabV3 segmenter trained on ISIC) rather than the gold ISIC masks
  themselves. This is the realistic deployment setting --- in practice the
  upstream segmenter is not perfect --- and it tests whether the lesion-focusing
  effect survives realistic mask noise.
  \item We use a clinically motivated operating point (specificity at
  $\geq 0.90$ sensitivity) and report \emph{bootstrap CIs} for every reported
  number, so claims about ``which input is better'' are properly hedged.
  \item We test cross-dataset generalization to PAD-UFES-20, whose imaging
  modality is fundamentally different (smartphone vs.\ dermoscope), and
  compare each model's HAM-trained, PAD-evaluated numbers under both input
  pipelines.
  \item \todo{Robustness-under-corruption experiment promised in the proposal
  (blur, noise, brightness shifts at several severities). Designed; not yet
  run. Slot reserved in \cref{sec:results}.}
  \item \todo{Error analysis. Currently planning: per-diagnosis confusion
  breakdown, and qualitative inspection of the cases where lesion-white flips
  the prediction relative to full-image, stratified by segmenter quality
  (Dice on the ISIC-style proxy mask).}
\end{enumerate}

% ============================================================================
\section{Results and Discussion}
\label{sec:results}

\subsection{Lesion segmentation}
The DeepLabV3-ResNet50 segmenter reaches test \textbf{Dice $0.909$} and
\textbf{IoU $0.857$} on the held-out ISIC 2018 Task 1 split.
\todo{Figure 1: 2$\times$4 grid of (input image, ground-truth mask, predicted
mask, lesion-white composite) on 4 representative HAM10000 images, including
one failure case where the segmenter under- or over-segments.}

\subsection{In-distribution classification (HAM10000 test set)}

\Cref{tab:ham_test} reports test sensitivity and specificity for every model on
the 1{,}464-image HAM10000 test set at the validation-tuned threshold. Each
cell is the bootstrap mean with the 95\% percentile CI.

\begin{table}[t]
\centering
\caption{HAM10000 test performance (n=1464). Threshold selected on validation
to hit sensitivity $\geq 0.90$; values are bootstrap mean (95\% CI) over 5000
resamples. ``Full'' = trained and tested on raw HAM10000 images; ``Lesion''
= trained and tested on the segmenter's lesion-on-white composites.}
\label{tab:ham_test}
\small
\begin{tabular}{lcccc}
\toprule
& \multicolumn{2}{c}{\textbf{Full image}} & \multicolumn{2}{c}{\textbf{Lesion-white}} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}
Model & Sens & Spec & Sens & Spec \\
\midrule
BasicCNN              & 0.836 (0.794, 0.879) & 0.727 (0.701, 0.752) & 0.911 (0.877, 0.943) & 0.694 (0.667, 0.720) \\
ViT (small)           & 0.844 (0.802, 0.884) & 0.726 (0.700, 0.751) & 0.864 (0.822, 0.902) & 0.681 (0.653, 0.707) \\
SimpleResNet          & 0.887 (0.848, 0.922) & 0.686 (0.659, 0.712) & 0.911 (0.877, 0.943) & 0.673 (0.646, 0.701) \\
Pretrained ResNet-50  & 0.847 (0.804, 0.885) & 0.815 (0.792, 0.837) & 0.877 (0.838, 0.913) & 0.801 (0.778, 0.824) \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Headline observations.}
\begin{itemize}
\item Lesion-white training \emph{raises sensitivity} for three of the four
backbones (BasicCNN: $0.836 \!\to\! 0.911$; SimpleResNet: $0.887 \!\to\!
0.911$; pretrained ResNet-50: $0.847 \!\to\! 0.877$), and the CIs for the
non-pretrained models are essentially disjoint from their full-image
counterparts.
\item Specificity is mostly \emph{unchanged or slightly worse} on lesion-white
inputs in-distribution, suggesting that the threshold is being pulled to a
more aggressive point to hit target sensitivity once the model has fewer
context cues to lean on.
\item The pretrained ResNet-50 is the strongest single model on either input
($\sim 0.80$ specificity at $\geq 0.85$ sensitivity), consistent with the
expectation that ImageNet features carry most of the heavy lifting on a
dataset of this size.
\end{itemize}

\subsection{Cross-domain generalization (PAD-UFES-20)}

\Cref{tab:pad_test} reports the same metrics when each HAM10000-trained model
is applied to PAD-UFES-20 (2{,}106 images, 1{,}627 malignant). The threshold
is the one chosen on the HAM10000 validation set --- it is \emph{not}
re-tuned for PAD-UFES-20 ---  because in deployment you do not have a
labeled PAD-UFES-20 set on which to recalibrate.

\begin{table}[t]
\centering
\caption{PAD-UFES-20 cross-domain performance (n=2106). Models trained only on
HAM10000 in the indicated image format and applied to PAD-UFES-20 without
recalibration. Bootstrap mean (95\% CI), 5000 resamples.}
\label{tab:pad_test}
\small
\begin{tabular}{lcccc}
\toprule
& \multicolumn{2}{c}{\textbf{Full image}} & \multicolumn{2}{c}{\textbf{Lesion-white}} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}
Model & Sens & Spec & Sens & Spec \\
\midrule
BasicCNN              & 0.453 (0.428, 0.477) & 0.785 (0.749, 0.820) & 0.504 (0.480, 0.528) & 0.868 (0.838, 0.899) \\
ViT (small)           & 0.785 (0.765, 0.805) & 0.476 (0.431, 0.519) & 0.746 (0.726, 0.768) & 0.476 (0.431, 0.520) \\
SimpleResNet          & 0.444 (0.420, 0.468) & 0.806 (0.769, 0.840) & 0.503 (0.479, 0.527) & 0.836 (0.802, 0.867) \\
Pretrained ResNet-50  & 0.622 (0.598, 0.645) & 0.766 (0.727, 0.805) & 0.669 (0.646, 0.692) & 0.622 (0.577, 0.665) \\
\midrule
Mean ensemble (4 models) & 0.578 (0.554, 0.602) & 0.829 (0.794, 0.861) & 0.635 (0.611, 0.658) & 0.781 (0.745, 0.817) \\
\midrule
\emph{ResNet trained on PAD (oracle)} & 0.898 (0.858, 0.934) & 0.611 (0.494, 0.722) & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{What we see.}
\begin{itemize}
\item Every HAM-trained model loses sensitivity dramatically on PAD-UFES-20
relative to its in-domain numbers, which is expected: the imaging modality has
changed completely (smartphone, no dermoscope), and PAD's class balance is
inverted relative to HAM's.
\item \textbf{Lesion-white inputs improve sensitivity} on the non-pretrained
backbones (BasicCNN $+5.1$pp, SimpleResNet $+5.9$pp, pretrained ResNet-50
$+4.7$pp), \emph{and} preserve or improve specificity for BasicCNN and
SimpleResNet (BasicCNN: $0.785\!\to\!0.868$). This is the cleanest support for
the lesion-focusing hypothesis in our data: when the background distribution
moves out of training, hiding the background helps.
\item The pretrained ResNet-50 is the exception on specificity: lesion-white
\emph{lowers} specificity from $0.766$ to $0.622$. \todo{Hypothesis to test:
ImageNet features already encode skin-like backgrounds well, so removing
context hurts more than it helps for this backbone. Check by measuring
penultimate-layer feature similarity between HAM and PAD with/without
lesion-white.}
\item The ViT is anomalous in both tables --- its $\sim 0.78$ PAD sensitivity
with $\sim 0.48$ specificity indicates it is predicting ``malignant'' for most
inputs, an artifact of the from-scratch training regime on a small dataset.
\todo{Decide whether to keep ViT in the headline tables or move to an
appendix.}
\item A mean-probability ensemble of all four classifiers is competitive with
the best single model on full images but loses to the pretrained ResNet-50
under lesion-white.
\end{itemize}

\paragraph{Reading PAD-trained ResNet (oracle row).}
For context we trained one model directly on PAD-UFES-20 and evaluated it on
PAD's own held-out test split ($n=317$). It reaches $0.898$ sensitivity and
$0.611$ specificity, with a wide specificity CI because the malignant class
dominates PAD's test split. This is a loose upper bound on what a cross-domain
HAM model could be expected to achieve.

\subsection{Robustness to image corruptions}
\todo{Designed in proposal but not yet run. Plan: apply Gaussian blur ($\sigma
\in \{0.5,1.0,2.0\}$), Gaussian noise ($\sigma \in \{0.02,0.05,0.10\}$), and
brightness shifts ($\pm \{0.1,0.2,0.3\}$) to the HAM10000 test set, score each
model on the corrupted set without retraining, and plot sensitivity and
specificity vs.\ corruption severity for full-image vs.\ lesion-white inputs.
Hypothesis: lesion-white inputs degrade more gracefully because corruption of
the (white) background contributes nothing to the prediction. Figure
placeholder: 2$\times$3 grid (corruption type $\times$ metric).}

\subsection{Error analysis}
\todo{Per-diagnosis confusion breakdown on HAM test, and a side-by-side panel
of cases where the lesion-white pipeline flips the prediction relative to
full-image (in both directions), stratified by predicted segmenter Dice on a
held-out ISIC-style validation. Looking specifically at: (i) does
lesion-white help on borderline mel/nv pairs? (ii) does it hurt when the
segmenter cuts off lesion edges?}

\subsection{Discussion and takeaways}
The matched-conditions comparison points to a nuanced answer. In-distribution
on HAM10000, lesion-focusing raises sensitivity but does not substantially
improve the operating-point specificity at $\geq 0.90$ sensitivity; the
networks were apparently already extracting most of the relevant signal from
the lesion itself. Under distribution shift to PAD-UFES-20, however,
lesion-focusing benefits the non-pretrained networks on \emph{both}
sensitivity and specificity, which is consistent with the shortcut-learning
hypothesis: when the background distribution moves, a classifier that never
saw background pixels has less to be confused by. The pretrained ResNet-50
is the partial exception, and we suspect its ImageNet prior partially
substitutes for the explicit context that lesion-focusing removes
(\todo{quantify}). The ViT trained from scratch on $\sim 10$k images is
underpowered and behaves as a near-constant ``malignant'' predictor under
shift; this is a known regime in which ViTs underperform CNNs without
either pretraining or heavy regularization.

% ============================================================================
\section{References}
\label{sec:refs}

\bibliographystyle{plainnat}
\bibliography{references}

% ============================================================================
\appendix
\section*{Reproducibility}
The code is at \url{TODO/github-link}. \verb|submit/submit_full_pipeline.sh|
chains data preparation, segmenter training, lesion-white image creation,
classifier training, cross-domain evaluation, and the bootstrap analysis as a
single SLURM job graph. \verb|src/training/ham10000_training.py| is the shared
trainer used by all four backbones; the per-config wrappers in
\verb|src/training/train_*.py| are 4-line shims. All experiments use seed 42.
W\&B logs: \todo{insert link or report ID}.

\section*{Team contributions}
\begin{itemize}
\item \textbf{Tobias Roemer.} Full-image baselines on HAM10000. Performance
evaluation framework. \todo{adjust to actual final split}
\item \textbf{Thomas Lee.} Lesion-white pipeline (segmenter $\to$ composite
$\to$ classifier). Cross-domain evaluation on PAD-UFES-20.
\item \textbf{Leo Li.} ISIC segmenter training. Robustness-under-corruption
experiment.
\end{itemize}

\end{document}
